Missing The Point

### 2020-09-22 Manuscript.Rmd
Data generation in each simulation run, 100 sims, 50 it
Set scientific estimate to 1 to compute coverage rates like they should

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results.Rdata")

@@

```{r}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.95) +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.2090) +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results_test.Rdata")

@@

```{r}
results %>% #filter(it>6) %>% 
  ggplot() +
  geom_hline(yintercept = 0.95, size = 2, color = "grey") +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>% 
  # filter(it>6) %>% 
  ggplot() +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

## Check if heuristic for AC works
```{r}
load("~/MissingThePoint/Data/convergence_diagnostics_test.Rdata")
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```
